Simulations

### 2025-12-12 simulations.qmd
added more tournaments

@@

@@

  # Validate input
  valid_structures <- c("singleElimination", "doubleElimination", "roundRobin", "groupStage", "stepLadder", "Repechage")
  if (!tournament_structure %in% valid_structures) {
    stop(paste("Invalid tournament_structure. Must be one of:", 
               paste(valid_structures, collapse = ", ")))
  }

@@

@@

   if (tournament_structure %in% c("Repechage")) {
    result <- process_tournament_type("Repechage", 
                                      repechege_param_grid, 
                                      repechege_key)
    results_list$Repechege <- result
  }

@@

  if (tournament_structure %in% c("groupStage")) {
    result <- process_tournament_type("groupStage", 
                                      group_stage_param_grid, 
                                      group_stage_key)
    results_list$groupStage <- result
  }
   if (tournament_structure %in% c("stepLadder")) {
    result <- process_tournament_type("stepLadder", 
                                      stepLadder_param_grid, 
                                      stepLadder_key)
    results_list$stepLadder <- result
  }

@@

compute_and_store_mi_by_tournament("singleElimination")
compute_and_store_mi_by_tournament("doubleElimination")
compute_and_store_mi_by_tournament("roundRobin")
compute_and_store_mi_by_tournament("groupStage")
compute_and_store_mi_by_tournament("stepLadder")
compute_and_store_mi_by_tournament("Repechage")

all_mi <- bind_rows(
  singleElimination_mi,
  doubleElimination_mi,
  groupStage_mi,
  roundRobin_mi,
  stepLadder_mi,
  Repechage_mi
)

all_mi_combinations <- bind_rows(
  singleElimination_combinations_mi,
  doubleElimination_combinations_mi,
  groupStage_combinations_mi,
  roundRobin_combinations_mi,
  stepLadder_combinations_mi,
  Repechage_combinations_mi
)
```

@@

```{r}
combined_plot_df <- plot_mi(all_mi, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups"
  )
)

@@

  # default group length
  group_length <- NA

@@

  return(data.frame(
    tournament_type = tournament_type,
    distribution = distribution,
    group_length = group_length
  ))
}

combined_plot_df <- combined_plot_df %>%
  select(-any_of(c("tournament_type", "distribution", "group_length"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_combined(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    # Create a label for the additional parameters
    param_label = paste(tournament_type, sep = "\n")
  )

combined_plot_df <- combined_plot_df %>%
  mutate(
    color_group = case_when(
      tournament_type == "groupStage" ~ "groupStage (4 Groups)",
      TRUE ~ tournament_type
    )
  )

@@

combined_combinations_df <- plot_mi(all_mi_combinations, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups"
  )
)

combined_combinations_df <- combined_combinations_df %>%
  select(-any_of(c("tournament_type", "distribution", "group_length"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_combined(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    # Create a label for the additional parameters
    param_label = paste(tournament_type, sep = "\n")
  )

combined_combinations_df <- combined_combinations_df %>%
  mutate(
    color_group = case_when(
      tournament_type == "groupStage" ~ "groupStage (4 Groups)",
      TRUE ~ tournament_type
    )
  )

@@

>>>>

```{r}
# Create separate parameter grids for each configuration
staged_rr_param_grid_4x4 <- expand.grid( 
  distribution = c("Normal", "Uniform", "Same", "Exponential"), 
  ties = c(FALSE, TRUE), 
  rounds = c(1, 2, 4),
  group_length = 4,
  grouping_mode = "by_rank",
  stringsAsFactors = FALSE
)

staged_rr_param_grid_2x8 <- expand.grid( 
  distribution = c("Normal", "Uniform", "Same", "Exponential"), 
  ties = c(FALSE, TRUE), 
  rounds = c(1, 2, 4),
  group_length = 8,
  grouping_mode = "by_pairs",
  stringsAsFactors = FALSE
)

# Combine both grids
staged_rr_param_grid <- rbind(staged_rr_param_grid_4x4, staged_rr_param_grid_2x8)

staged_rr_run_sim_block <- function(
  teams, distribution, ties, rounds, group_length, grouping_mode, p_block) {

  # Build the key
  parts <- c(
    "stagedRR",
    tolower(distribution),
    ifelse(ties, "ties", "noTies"),
    paste0("r", rounds),
    paste0("g", group_length)
  )
  key <- paste(parts, collapse = "_")

  # Run simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_staged_rr(
        num_teams = teams,
        distribution = distribution,
        ties = ties,
        rounds = rounds,
        group_length = group_length,
        grouping_mode = grouping_mode
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

# Run the simulations with progress bar
with_progress({
  p_block <- progressor(steps = nrow(staged_rr_param_grid))

  for (i in seq_len(nrow(staged_rr_param_grid))) {
    row <- staged_rr_param_grid[i, ]

    staged_rr_run_sim_block(
      teams        = teams, 
      distribution = row$distribution,
      ties         = row$ties,
      rounds       = row$rounds,
      group_length = row$group_length,
      grouping_mode = row$grouping_mode,
      p_block = p_block
    )
  }
})

@@

```{r}
tennis_ladder_param_grid <- expand.grid( 
  distribution = c("Normal","Uniform", "Same", "Exponential"), 
  r = c(5,10,15),
  bad_seeding_structure = c(FALSE, TRUE) 
  )

tennis_ladder_run_sim_block <- function(
  teams, distribution, ties, r, p_block, bad_seeding_structure) {

  # Apply bad seeding structure override if required
  seeding_structure <- if (bad_seeding_structure) 16:1 else NULL

  # Build key
    # Build the key
  parts <- c(
    "tennisLadder",
    tolower(distribution),
    paste0(r),
    if (bad_seeding_structure) "badseed"
  )

  # Run 10,000 simulations in parallel
  sim_list <- future_lapply(
    X = 1:10000,
    FUN = function(rep) {
      simulate_tennis_ladder(
        num_teams = teams,
        distribution = distribution,
        r = r,
        seeding_structure = seeding_structure
      )
    },
    future.seed = TRUE    # ensures parallel RNG is valid
  )

with_progress({
  p_block <- progressor(steps = nrow(tennis_ladder_param_grid))

  for (i in seq_len(nrow(tennis_ladder_param_grid))) {
    row <- tennis_ladder_param_grid[i, ]

    tennis_ladder_run_sim_block(
      teams        = teams,
      distribution = row$distribution,
      r            = row$r,
      bad_seeding_structure = row$bad_seeding_structure,
      p_block = p_block
    )
  }
})
```

@@

  # Validate input
  valid_structures <- c("singleElimination", "doubleElimination", "roundRobin", 
                       "groupStage", "stepLadder", "Repechage", "stagedRR", "tennisLadder")
  if (!tournament_structure %in% valid_structures) {
    stop(paste("Invalid tournament_structure. Must be one of:", 
               paste(valid_structures, collapse = ", ")))
  }

@@

  tennisLadder_key <- function(row, type) {
    c(
      type,
      tolower(row$distribution),
      paste0(row$r),
      if (row$bad_seeding_structure) "badseed"
    )
  }

  # Key builders for stagedRR (both configurations)
  staged_rr_4x4_key <- function(row, type) {
    c(
      type,
      tolower(row$distribution),
      ifelse(row$ties, "ties", "noTies"),
      paste0("r", row$rounds),
      paste0("g", row$group_length)
    )
  }

  staged_rr_2x8_key <- function(row, type) {
    c(
      type,
      tolower(row$distribution),
      ifelse(row$ties, "ties", "noTies"),
      paste0("r", row$rounds),
      paste0("g", row$group_length)
    )
  }

@@

  if (tournament_structure %in% c("Repechage")) {
    result <- process_tournament_type("Repechage", 
                                      repechege_param_grid, 
                                      repechege_key)
    results_list$Repechage <- result
  }

@@

  if (tournament_structure %in% c("groupStage")) {
    result <- process_tournament_type("groupStage", 
                                      group_stage_param_grid, 
                                      group_stage_key)
    results_list$groupStage <- result
  }

  if (tournament_structure %in% c("stepLadder")) {
    result <- process_tournament_type("stepLadder", 
                                      stepLadder_param_grid, 
                                      stepLadder_key)
    results_list$stepLadder <- result
  }

  # Process stagedRR - combined approach using full param grid
  if (tournament_structure %in% c("stagedRR")) {
    # Use the combined param grid and a unified key builder
    result <- process_tournament_type("stagedRR", 
                                      staged_rr_param_grid,
                                      staged_rr_4x4_key)  # Works for both since key structure is same
    results_list$stagedRR <- result
  }

  if (tournament_structure %in% c("tennisLadder")) {
    result <- process_tournament_type("tennisLadder", 
                                      tennis_ladder_param_grid, 
                                      tennisLadder_key)
    results_list$tennisLadder <- result
  }

@@

# Run computations for all tournament types
compute_and_store_mi_by_tournament("singleElimination")
compute_and_store_mi_by_tournament("doubleElimination")
compute_and_store_mi_by_tournament("roundRobin")
compute_and_store_mi_by_tournament("groupStage")
compute_and_store_mi_by_tournament("stepLadder")
compute_and_store_mi_by_tournament("Repechage")
compute_and_store_mi_by_tournament("stagedRR")
compute_and_store_mi_by_tournament("tennisLadder")

# Combine all MI results
all_mi <- bind_rows(
  singleElimination_mi,
  doubleElimination_mi,
  groupStage_mi,
  roundRobin_mi,
  stepLadder_mi,
  Repechage_mi,
  stagedRR_mi,
  tennisLadder_mi
)

# Combine all MI combinations results
all_mi_combinations <- bind_rows(
  singleElimination_combinations_mi,
  doubleElimination_combinations_mi,
  groupStage_combinations_mi,
  roundRobin_combinations_mi,
  stepLadder_combinations_mi,
  Repechage_combinations_mi,
  stagedRR_combinations_mi,
  tennisLadder_combinations_mi
)
```

@@

```{r}
combined_plot_df <- plot_mi(all_mi, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups",
  "stagedRR_normal_noTies_r1_g4",
  "stagedRR_uniform_noTies_r1_g4",
  "stagedRR_same_noTies_r1_g4",
  "stagedRR_exponential_noTies_r1_g4",
  "tennisLadder_normal_15",
  "tennisLadder_uniform_15",
  "tennisLadder_same_15",
  "tennisLadder_exponential_15"
  )
)

@@

  # default group length/rounds
  group_length <- NA
  rounds <- NA

@@

  if(tournament_type == "stagedRR"){
    group_length <- as.numeric(str_extract(parts[5], "\\d+"))
    rounds <- as.numeric(str_extract(parts[4], "\\d+"))
  }

  if(tournament_type == "tennisLadder"){
    rounds <- as.numeric(parts[3])
  }

  return(data.frame(
    tournament_type = tournament_type,
    distribution = distribution,
    group_length = group_length,
    rounds = rounds
  ))
}

combined_plot_df <- combined_plot_df %>%
  select(-any_of(c("tournament_type", "distribution", "group_length", "rounds"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_combined(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    # Create a label for the additional parameters
    param_label = paste(tournament_type, sep = "\n")
  )

combined_plot_df <- combined_plot_df %>%
  mutate(
    color_group = case_when(
      tournament_type == "groupStage" ~ "groupStage (4 Groups)",
      tournament_type == "stagedRR" ~ "stagedRR (4 Groups)",
      tournament_type == "tennisLadder" ~ "tennisLadder (15 Rounds)",
      TRUE ~ tournament_type
    )
  )

@@

combined_combinations_df <- plot_mi(all_mi_combinations, c(
  "singleElimination_normal_noTies_1",
  "singleElimination_uniform_noTies_1", 
  "singleElimination_same_noTies_1", 
  "singleElimination_exponential_noTies_1",
  "doubleElimination_normal_noTies_1", 
  "doubleElimination_uniform_noTies_1",
  "doubleElimination_same_noTies_1", 
  "doubleElimination_exponential_noTies_1", 
  "roundRobin_normal_noTies_1", 
  "roundRobin_uniform_noTies_1", 
  "roundRobin_same_noTies_1", 
  "roundRobin_exponential_noTies_1", 
  "groupStage_normal_noTies_1_4groups",
  "groupStage_uniform_noTies_1_4groups",
  "groupStage_same_noTies_1_4groups",
  "groupStage_exponential_noTies_1_4groups",
  "stagedRR_normal_noTies_r1_g4",
  "stagedRR_uniform_noTies_r1_g4",
  "stagedRR_same_noTies_r1_g4",
  "stagedRR_exponential_noTies_r1_g4",
  "tennisLadder_normal_15",
  "tennisLadder_uniform_15",
  "tennisLadder_same_15",
  "tennisLadder_exponential_15"
  )
)

combined_combinations_df <- combined_combinations_df %>%
  select(-any_of(c("tournament_type", "distribution", "group_length", "rounds"))) %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_dataset_name_combined(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    # Create a label for the additional parameters
    param_label = paste(tournament_type, sep = "\n")
  )

combined_combinations_df <- combined_combinations_df %>%
  mutate(
    color_group = case_when(
      tournament_type == "groupStage" ~ "groupStage (4 Groups)",
      tournament_type == "stagedRR" ~ "stagedRR (4 Groups)",
      tournament_type == "tennisLadder" ~ "tennisLadder (15 Rounds)",
      TRUE ~ tournament_type
    )
  )

@@

```{r}
staged_rr_plot_df <- plot_mi(stagedRR_mi)

# Parse dataset names to extract parameters for staged RR
parse_staged_rr_name <- function(dataset_name) {
  parts <- str_split(dataset_name, "_")[[1]]

  # Extract ties (third part)
  ties <- ifelse(parts[3] == "noTies", "No Ties", "Ties")

  # Extract rounds (fourth part - extract number after 'r')
  rounds <- as.numeric(str_extract(parts[4], "\\d+"))

  # Extract group length (fifth part - extract number after 'g')
  group_length <- as.numeric(str_extract(parts[5], "\\d+"))

# Add parameter columns to the plot data
staged_rr_plot_df <- staged_rr_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_staged_rr_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(rounds, levels = c(1, 2, 4)),
    # Create a label for the additional parameters
    param_label = paste(group_length, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
staged_rr_plot_df <- staged_rr_plot_df %>%
  mutate(
    color_group = paste(group_length, sep = " | ")
  )

# Filter data for No Ties
staged_rr_noties_df <- staged_rr_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
staged_rr_ties_df <- staged_rr_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties
staged_rr_noties_plot <- ggplot(staged_rr_noties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Staged RR: Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Ties
staged_rr_ties_plot <- ggplot(staged_rr_ties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Staged RR: Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

staged_rr_combinations_plot_df <- plot_mi(stagedRR_combinations_mi)

# Add parameter columns to the plot data
staged_rr_combinations_plot_df <- staged_rr_combinations_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_staged_rr_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    series = factor(rounds, levels = c(1, 2, 4)),
    # Create a label for the additional parameters
    param_label = paste(group_length, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
staged_rr_combinations_plot_df <- staged_rr_combinations_plot_df %>%
  mutate(
    color_group = paste(group_length, sep = " | ")
  )

# Filter data for No Ties
staged_rr_combinations_noties_df <- staged_rr_combinations_plot_df %>%
  filter(ties == "No Ties")

# Filter data for Ties
staged_rr_combinations_ties_df <- staged_rr_combinations_plot_df %>%
  filter(ties == "Ties")

# Plot 1: No Ties (Combinations)
staged_rr_combinations_noties_plot <- ggplot(staged_rr_combinations_noties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Staged RR (Combinations): Mutual Information (No Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Ties (Combinations)
staged_rr_combinations_ties_plot <- ggplot(staged_rr_combinations_ties_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    series ~ distribution,
    labeller = labeller(
      series = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Staged RR (Combinations): Mutual Information (Ties)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Group Length:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Display plots
print(staged_rr_noties_plot)
print(staged_rr_ties_plot)

# Display plots
print(staged_rr_combinations_noties_plot)
print(staged_rr_combinations_ties_plot)
```

## Tennis Ladder

```{r}
tennis_ladder_plot_df <- plot_mi(tennisLadder_mi)

# Parse dataset names to extract parameters for tennis ladder
parse_tennis_ladder_name <- function(dataset_name) {
  parts <- str_split(dataset_name, "_")[[1]]

  # Extract rounds (third part - the number)
  rounds <- as.numeric(parts[3])

  # Check if it's a "badseed" variant (fourth part)
  seed_type <- ifelse(length(parts) >= 4 && parts[4] == "badseed", "Bad Seed", "Good Seed")

  return(data.frame(
    distribution = distribution,
    rounds = rounds,
    seed_type = seed_type
  ))
}

# Add parameter columns to the plot data
tennis_ladder_plot_df <- tennis_ladder_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_tennis_ladder_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    rounds_factor = factor(rounds, levels = c(5, 10, 15)),
    # Create a label for the additional parameters
    param_label = paste(rounds, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
tennis_ladder_plot_df <- tennis_ladder_plot_df %>%
  mutate(
    color_group = paste(rounds, sep = " | ")
  )

# Filter data for Good Seed
tennis_ladder_goodseed_df <- tennis_ladder_plot_df %>%
  filter(seed_type == "Good Seed")

# Filter data for Bad Seed
tennis_ladder_badseed_df <- tennis_ladder_plot_df %>%
  filter(seed_type == "Bad Seed")

# Plot 1: Good Seed
tennis_ladder_goodseed_plot <- ggplot(tennis_ladder_goodseed_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    rounds_factor ~ distribution,
    labeller = labeller(
      rounds_factor = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Tennis Ladder: Mutual Information (Good Seed)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Rounds:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Bad Seed
tennis_ladder_badseed_plot <- ggplot(tennis_ladder_badseed_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    rounds_factor ~ distribution,
    labeller = labeller(
      rounds_factor = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Tennis Ladder: Mutual Information (Bad Seed)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Rounds:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

tennis_ladder_combinations_plot_df <- plot_mi(tennisLadder_combinations_mi)

# Add parameter columns to the plot data
tennis_ladder_combinations_plot_df <- tennis_ladder_combinations_plot_df %>%
  group_by(dataset) %>%
  mutate(
    params = list(parse_tennis_ladder_name(dataset[1]))
  ) %>%
  unnest(params) %>%
  ungroup() %>%
  mutate(
    rounds_factor = factor(rounds, levels = c(5, 10, 15)),
    # Create a label for the additional parameters
    param_label = paste(rounds, sep = "\n")
  )

# Create a consistent color variable based on the parameter combinations
tennis_ladder_combinations_plot_df <- tennis_ladder_combinations_plot_df %>%
  mutate(
    color_group = paste(rounds, sep = " | ")
  )

# Filter data for Good Seed
tennis_ladder_combinations_goodseed_df <- tennis_ladder_combinations_plot_df %>%
  filter(seed_type == "Good Seed")

# Filter data for Bad Seed
tennis_ladder_combinations_badseed_df <- tennis_ladder_combinations_plot_df %>%
  filter(seed_type == "Bad Seed")

# Plot 1: Good Seed (Combinations)
tennis_ladder_combinations_goodseed_plot <- ggplot(tennis_ladder_combinations_goodseed_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    rounds_factor ~ distribution,
    labeller = labeller(
      rounds_factor = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Tennis Ladder (Combinations): Mutual Information (Good Seed)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Rounds:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Plot 2: Bad Seed (Combinations)
tennis_ladder_combinations_badseed_plot <- ggplot(tennis_ladder_combinations_badseed_df, aes(x = index, y = mi_values, color = color_group, group = dataset)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  facet_grid(
    rounds_factor ~ distribution,
    labeller = labeller(
      rounds_factor = function(x) paste("Rounds:", x),
      distribution = function(x) x
    )
  ) +
  labs(
    title = "Tennis Ladder (Combinations): Mutual Information (Bad Seed)",
    x = "Top K Teams",
    y = "Mutual Information (MI)",
    color = "Rounds:"
  ) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_x_continuous(breaks = 1:16) + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 8),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom", 
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    panel.spacing = unit(1, "lines")
  ) +
  scale_color_d3("category20") +
  guides(color = guide_legend(nrow = 1))

# Display plots
print(tennis_ladder_goodseed_plot)
print(tennis_ladder_badseed_plot)

# Display plots
print(tennis_ladder_combinations_goodseed_plot)
print(tennis_ladder_combinations_badseed_plot)
```
